On the replication of Sobol' sequences to estimate main effects of model inputs

### 2016-04-02 replicated_sobol.tex
Fixing typo x_{i,u}=x_{i,u+s}

The only constraint we have is that for each $u=1,\dots,s$, the $2s$-dimensional Sobol' sequence must ensure that $x_{i,u}=x_{i,u}$ for $i\in\mathbb{N}_0$. Therefore, we will need $s$ different $2s$-dimensional sequences. These sequences can be constructed using a single $2s$-dimensional sequence and considering the corresponding upper triangular matrices $U_u$.

Given the generators $C_1,\dots,C_s,C'_1,\dots,C'_s$, we  define the $U_u$ matrices such that $C_u=C'_uU_u$. Then, each sequence generated by $C_1,\dots,C_s,C'_1U_u,\dots,C'_sU_u$ will satisfy $x_{i,u}=x_{i,u}$, for all $i\in\mathbb{N}_0$.

>>>>

The only constraint we have is that for each $u=1,\dots,s$, the $2s$-dimensional Sobol' sequence must ensure that $x_{i,u}=x_{i,u+s}$ for $i\in\mathbb{N}_0$. Therefore, we will need $s$ different $2s$-dimensional sequences. These sequences can be constructed using a single $2s$-dimensional sequence and considering the corresponding upper triangular matrices $U_u$.

Given the generators $C_1,\dots,C_s,C'_1,\dots,C'_s$, we  define the $U_u$ matrices such that $C_u=C'_uU_u$. Then, each sequence generated by $C_1,\dots,C_s,C'_1U_u,\dots,C'_sU_u$ will satisfy $x_{i,u}=x_{i,u+s}$, for all $i\in\mathbb{N}_0$.
